A Critical Appraisal of Zero-Multiple Method in Simulation Biomolecular Systems

### 2014-05-21 writedown/zm/report/report.tex
add table for result of some numbers

\subsubsection{Pressure}
The results are plotted in Fig.~\ref{fig:tmp0}.
\begin{figure}
  \centering
  \includegraphics[]{pressure-methods.eps}
  \caption{The pressure convergence with respect to the cut-off radius.
    For ZM method, the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
  }
  \label{fig:tmp0}
\end{figure}

@@

@@

\begin{figure}
  \centering
  \includegraphics[]{fig-gkr-small.eps}
  \includegraphics[]{fig-gkr-small-conv.eps}
  \caption{The Kirkwood G-factor calculated for system S1.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{fig-gkr.eps}
  \includegraphics[]{fig-gkr-conv.eps}
  \caption{The Kirkwood G-factor calculated for system L1.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp2}
\end{figure}

>>>>

\subsubsection{Pressure}
The results are plotted in Fig.~\ref{fig:tmp0}. All pressure calculations are done with system L0.
\begin{figure}
  \centering
  \includegraphics[]{pressure-methods.eps}
  \caption{The pressure convergence with respect to the cut-off radius.
    For ZM method, the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
  }
  \label{fig:tmp0}
\end{figure}

@@

\begin{table}
  \centering
  \caption{A list of the dielectric constant calculated for different systems by different methods.
    The paremeters are provided. The parenthesises in the last column show the statistical uncertanty
    of the last two digits upto the confidence level of 95~\%.}
  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cccc rrrr}\hline\hline
    Method      &   $r_c$ [nm] &    $l$     &  $\mu$ [kJ/mol] & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] & $C_v$ [J/(mol K)] & $\eps$ & $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
    SPME        &         1.9     &       --      &       $-26.08$ (0.24) & 5.93 (0.42)   & 72.21 (0.97)  & 97.6 (3.4)  & 0.315 (0.007)\\
    RF          &         1.2     & -- & $-26.03$   (0.32)    & 6.27 (0.11)   & 72.28 (0.81)  & 59.4  (1.3)     & 0.449 (0.020) \\
    ZM          &         1.2     &       1       &       $-26.12$ (0.30) & 5.55 (0.02)   & 71.75 (0.89)  & 95.5 (2.4)  & 0.346 (0.006)\\ 
    ZM          &         1.2     &       2       &       $-26.00$ (0.24) & 5.72 (0.37)   & 71.53 (0.88)  & 95.4 (2.5)  & 0.318 (0.012)\\ 
    ZM          &         1.2     &       3       &       $-25.76$ (0.20) & 5.82 (0.12)   & 71.58 (0.88)  & 96.0 (2.7)  & 0.321 (0.008)\\ 
    ZM          &         1.2     &       4       &       $-25.37$ (0.26) & 5.92 (0.08)   & 71.07 (0.84)  & 99.7 (2.2)  & 0.318 (0.013)\\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp2}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig-gkr-small.eps}
  \includegraphics[]{fig-gkr-small-conv.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-3000.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-3000.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-10000.eps}
  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-10000.eps}
  \caption{The Kirkwood G-factor calculated for system S1.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{fig-gkr.eps}
  \includegraphics[]{fig-gkr-conv.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-3000.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-3000.eps}
  \caption{The Kirkwood G-factor calculated for system L1.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp2}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{fig-gkr-10000.eps}
  \includegraphics[]{fig-gkr-conv-10000.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-10000.eps}
  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-10000.eps}
  \caption{The Kirkwood G-factor calculated for system L1. Equilibriation time is 10~ns, and the production simulation time is 10~ns.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp3}
\end{figure}
